A GPU Implementation of Capon for an Active Sonar System

### 2012-05-03 ECUA2012/gpu_capon_ecua2012.tex
la2pdf commit - 2012:05:03	13:56:31	(Thu 3.May)

% - Who's done stuff on GPU beamforming before?
% 
% - Complex data
% -

@@

>>>>

\todo{Get some references in here...}
% - Who's done stuff on GPU beamforming before?
% 
% - Complex data
% -

@@

\section{Results}

Benchmarks were carried out on a test system comprised of a quad-core Intel Xeon E5620 running at 2.4GHz, 64Gb of \gls{RAM}, and an nVidia Quadro 6000 card. This \gls{GPU}

To test the \gls{CUDA} implementation of the \gls{MVDR} beamformer, we have chosen a dataset from the $M=32$ element Kongsberg Maritime HISAS1030 sonar~\cite{Hansen2009}. \todo{Data???}.
